decompr article

### 2014-12-01 README.Rmd
add examples

@@

Wang Wei Zhu
-------------------
 * Small derivation
 * R demonstration using WIOD data
 *

@@

Input and Output Data
----------------------

>>>>

```{r load-package, echo=FALSE}
library(decompr)
```

@@

A sample dataset of Input-Output tables is included.
In order to save space and speed up computations, the included dataset uses regional aggregates.

Load the included dataset of WIOD regional Input-Output tables.
```{r load-data}
data(wiod)
```

A key step in loading the data is making sure that the dimensions of the data inputs are correct,
in the sample data we have **G = 7** (generally countries, here regions) and **N = 43** (number of industries).
```{r data-dimensions}
dim(intermediate_demand) # (2 + GN + totals) x (2 + GN)
dim(final_demand)        # (2 + GN + totals) x (2 + G*5)
```

Note thata **G** and **N** are automatically inferred from the dimensions of the data.

When importing data, be sure to specify **stringsAsFactors = FALSE** and to **header=FALSE**,
as the Input-Output tables use two header lines (country and industry),

Wang Wei Zhu
-------------------
 * Small derivation
 * R demonstration using WIOD data

```{r load_tables}
elements <- load_tables( x = intermediate_demand,
                         y = final_demand         )
```

We can now decompose the elements using the Wang-Wei-Zhu (or source) decomposition.
```{r wwz}
wwz <- wwz( elements )
```

In addition, a wrapper function called **decomp** is provided which performs both steps at once.
Though it is recomended that the seperate functions be used for large data sets.

```{r wwz-wrapper}
wwz2 <- decomp( x = intermediate_demand,
                y = final_demand,
                method = "wwz"           )
```

Note that **wwz** is the default method.

The output data is as follows

```{r wwz-eval}
str(wwz)
```

@@

We can now decompose the elements using the Source decomposition.
```{r source}
source <- kung_fu( elements )
```

In addition, a wrapper function called **decomp** is provided which performs both steps at once.
Though it is recomended that the atomic functions be used for large data sets.

```{r source-wrapper}
source2 <- decomp( x = intermediate_demand,
                y = final_demand,
                method = "source"           )
```

The output data is as follows

```{r source-eval}
str(source)
```
